Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex

\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
\newcommand*\justify{%
  \fontdimen2\font=0.4em% interword space
  \fontdimen3\font=0.2em% interword stretch
  \fontdimen4\font=0.1em% interword shrink
  \fontdimen7\font=0.1em% extra space
}

@@

\begin{abstract}
To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context. In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e. when executing the same search at different times, the same encyclopedia entities are returned.
\end{abstract}

@@

On microblogging platforms it is possible to search for messages containing a specific hash tag. This search returns a fixed number of most recent messages containing the tag. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.

@@

Furthermore, this annotation will help to understand hash tags. Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms. For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$. If a user encounters this hash tag and does not understand it, he can search for it on the microblogging platform. However, as discussed before, to understand a search result is difficult and time-consuming. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These entities will help the user to gain an understanding in which context the hash tag is used and what it may mean. If a hash tag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hash tag. A system may be envisioned which automatically finds entitities which are equivalent to a hash tag. Thus, these hash tag-entity pairs may be used similarly to systems in which hash tags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.

Finding entities matching a query, especially a query for a given hash tag is difficult due to synonyms and homonyms in the set of hash tags that are frequently used. For example, both the hash tags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe. The tag $\#ka$ is however also used in the context of the car type Ford Ka. Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka. An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.

In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities. While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for the annotation tool. Thus, we chose to generate annotations for the whole search result.

The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia. The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}). Note however that a direct mapping of hash tags to entities is not possible in many cases: e.g. there is no entity in dbpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.

Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change. In an evaluation of our approach we have tried to analyze the stability of the result.

Our contributions thus are:
\begin{itemize}
	\item an approach for finding entities which are related to a search on microblogging platforms
	\item a formatting of microblogging messages as RDF
	\item an implementation of our approach
	\item an evaluation of the stability and relevance of the entities found with our approach.
\end{itemize}

@@

The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter. Thus, an automatic way of mapping the Twitter social network to semantic data is made available.

Passant et al. \cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web. They propose a data model which allows for the association of URIs with users, microblogs and microposts. To this end, SIOC and FOAF vocabularies are used and extended. Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced. Additionally, they propose the use of so-called semantic hash tags. The idea is to use URIs as hash tags (e.g. \emph{\#geo:Paris\_France}). It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags. 
In contrast to this approach we do not require users to change their behavior by requiring them to use another type of hash tags. Instead, our method finds Linked Open Data entities which are related to the query automatically.

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.

Relating semantic concepts with twitter messages has been attempted by various authors:
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.
Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.

Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.

Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts. We too use external data to augment the set of Twitter messages supplied to the Wikifier system.

The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.

@@

The goal of our method is to, given a search query $q$ as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e. the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result.

The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
receipt of a query four steps are performed. In the following we will illustrate
these steps using the example of a search for the hash tag $\#Libya$, a hashtag
which is frequently used to describe posts related to the country of Libya.

@@

\begin{enumerate}
	\item In a first step, the most recent search results for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
	return a document containing all most recent Twitter posts whose content
	matched the search string $\#Libya$ and their meta information. 
	\newline
	An
example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
for a single retrieved post is the following:\newline\texttt{\justify{"Arab
League calls for no-fly zone in \#Libya http://t.co/ZsLNIWa"}},\newline posted
by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
the text found at the link should return the following text:\newline
\texttt{\justify{"Arab League calls for Libya no-fly zone-state TV
- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
Security Council to impose a no-fly zone on Libya, Egyptian state television
reported, a decision that would give a regional seal of approval that NATO has
said is needed for any military action."}}
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#Libya'
are merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream:\newline\texttt{\justify{"Arab
League calls for no-fly zone in \#Libya Arab League calls for Libya no-fly zone-state TV
- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
Security Council to impose a no-fly zone on Libya, Egyptian state television
reported, a decision that would give a regional seal of approval that NATO has
said is needed for any military action."}}\newline This string is appended to
the Twitter content and the external content of all other posts in the result.

@@

	\item	Finally, an RDF document is generated representing the search results and
	the annotations. \newline
	Continuing our example, the output RDF document should contain the following
	triples to reference the DBPedia mappings:\newline
    \texttt{\justify{<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap?q\newline=\%23lybia>
    rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,\newline
    <http://dbpedia.org/resource/Gaddafi> ,\newline
    <http://dbpedia.org/resource/Arab\_League> .}}\newline
	The Twitter posts matching the search term \#Libya are likewise all described
	in the output document. Here, the description for the initially given post
	abbreviated \texttt{m} results in the following
	triples:\newline
	\texttt{\justify{<http://km.aifb.kit.edu/services/twitterwrap/statuses/show/4661\newline
	9460060196865\#id> foaf:page
	<http://twitter.com/SenJohnMcCain/\newline statuses/46619460060196865>
	;\newline dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;\newline geo:long "8.411879" ;\newline foaf:maker
	<http://km.aifb.kit.edu/services/twitterwrap/users/\newline
	 show?screen\_name=SenJohnMcCain\#id> ;\newline dc:description "Arab League
	calls for no-fly zone in \#Libya http://\newline t.co/ZsLNIWa" . }}

\end{enumerate}

@@

In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.

The implementation is based on a set of existing components: Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}. The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors. The messages themselves are described by their content, publishing date, authors
and optionally a geographic location.

The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true} in our
system. To keep the input size for the next steps manageable, we do not use the
whole content of the referenced sites but only the first 50 words. The content
retrieved from external websites is beautified for our purpose removing
HTML-tags and scripting elements using the CyberNeko Java HTML Parser
Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.

The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.

The system generates and outputs an RDF document in RDF/XML Syntax containing a
description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
Vocabulary \cite{key:geo}. A single twitter message is described by its
individual page using \texttt{foaf:page} predicate. The date and time the
message has been posted is specified using \texttt{dc:date} predicate. The messages content
is annotated using \texttt{dc:description}, while the geographic location of the
message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
uses RDF to describe information related to a Twitter user which has previously
been implemented here at the institute as the message creators URI.

@@

%The example twitter message given in the previous section is represented in
%the output of the Twitter Search Wrapper as follows:\newline
%\linebreak
%\texttt{<rdf:Description
%rdf:about="http://km.aifb.kit.edu/services/\newline
%twitterwrap/statuses/show/1234567890\#id">\newline
%	<foaf:page
%	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
%	statuses/1234567890"/>\newline
%	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
%	<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
%	<foaf:maker
%	rdf:resource="http://km.aifb.kit.edu/services/\newline
%	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline
%	<dc:description>\newline Just returned from a wonderful holiday in \#ka.
%	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
%	</dc:description>\newline
%	</rdf:Description>\newline}
%	\linebreak
%Furthermore the mappings to DBpedia articles returned by the Wikifier
%are represented in the output document. In the Twitter Search Wrapper the
%representation is done the following way, again using the introductory
%example from the previous section:\newline
%\linebreak
%	\texttt{<rdf:Description rdf:about=""/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
%	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
%	Karlsruhe\_Institute\_of\_Technology"/>}\newline
%	\texttt{</rdf:Description>}\newline

@@

We have evaluated our approach to assess whether the entities which are found as related to a specific hash tag are useful and stable over time.

@@

We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}. Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Trending Topics Worldwide  \\
\hline
\#goodlucknickj  \\
\#smalljoys \\
\#thingsthedevilinvented \\
Adam Wainwright  \\
CatchPetrovaFire \\
Gadafi  \\
Libia \\
Precious Minaj \\
Tommy John  \\
\end{tabular}
\begin{tabular}{l}
Trending Topics Germany \\
\hline
\#gaddafi \\
\#guttenberg  \\
\#libya  \\
Doktorarbeit \\
Gef\"{u}hl  \\
Lion  \\
MBP \\
Thunderbolt \\
Vorratsdatenspeicherung \\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

The second query set consists of hash tags that are frequently used on Twitter.
To obtain these, we have sampled the Twitter message feed using Twitter's
Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
top-50 hashtags dervied from the aggregate sample are listed in Table
\ref{tbl:hashtags}, count is the number of times we encountered them during the
collection period.

@@

@@

ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
nowplaying & 144 & 17 & 0.4514 & 0.0251 & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\
rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\
partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\
damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\
quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\

@@

nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\

>>>>

\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
%\newcommand*\justify{%
%  \fontdimen2\font=0.4em% interword space
%  \fontdimen3\font=0.2em% interword stretch
%  \fontdimen4\font=0.1em% interword shrink
%  \fontdimen7\font=0.1em% extra space
%}

@@

\begin{abstract}
Microblog messages contain so-called hashtags which are usedto mark keywords or topics. To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context. In an evaluation we analyse the stability of the related entities.
\end{abstract}

@@

On microblogging platforms it is possible to search for messages containing a specific hashtag. This search returns a fixed number of most recent messages containing the tag. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.

@@

Furthermore, this annotation will help to understand hashtags. Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms. For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$. If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform. However, understanding a search result is difficult and time-consuming. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean. If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag. A system may be envisioned which automatically finds entitities which are equivalent to a hashtag. Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.

Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message. Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used. For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe. The tag $\#ka$ is however also used in the context of the car type Ford Ka. Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka. An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.

In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities. While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}. Thus, we chose to generate annotations for the whole search result.

The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia. The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}). External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible. Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g. there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.

Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change. In an evaluation of our approach we have tried to analyse the stability of the result.

Our contributions thus are:
\begin{itemize}
	\item We present an approach for finding entities which are related to search results on microblogging platforms
	\item We specify a formatting of microblogging messages as RDF
	\item We evaluate the stability of the found entities.
\end{itemize}

@@

@@

The goal of our method is to, given a search query $q$ as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e. the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result. 
In the following we will illustrate our approach based on a search for the hashtag $\#Libya$, a hashtag
which is frequently used to describe posts related to the country of Libya.

The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
receipt of a query $q$ four steps are performed.

@@

\begin{enumerate}
	\item In a first step, the most recent search results $R$ for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
	return a document containing all most recent Twitter posts whose content
	matched the search string $\#Libya$ and their meta information. 
	\newline
	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
for a single retrieved post is the following:
{\small
\begin{verbatim}
"Arab League calls for no-fly zone in #Libya http://t.co/ZsLNIWa"
\end{verbatim}}
This messageposted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
the text found at the link should return the following text:
{\small\begin{verbatim}"Arab League calls for Libya no-fly zone-state TV - CAIRO, March 12
(Reuters) - The Arab League on Saturday called on the U.N. Security 
Council to impose a no-fly zone on Libya, Egyptian state television
reported, a decision that would give a regional seal of approval
that NATO has said is needed for any military action."\end{verbatim}}
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#Libya'
are merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream:
\begin{verbatim}"Arab League calls for no-fly zone in #Libya
Arab League calls for Libya no-fly zone-state TV - CAIRO, 
March 12 (Reuters) - The Arab League on Saturday called on the 
U.N. Security Council to impose a no-fly zone on Libya, 
Egyptian state television reported, a decision that would give
a regional seal of approval that NATO has said is needed for 
any military action."\end{verbatim}
This string is appended to the Twitter content and the external content of all other posts in the result.

@@

	\item	Finally, an RDF document is generated representing the search results and
	the annotations. Continuing our example, the output RDF document should contain the following
	triples to reference the DBPedia mappings:
	{\small\begin{verbatim}	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
	?q=\%23lybia>
     rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,
        <http://dbpedia.org/resource/Gaddafi> ,
        <http://dbpedia.org/resource/Arab\_League> .\end{verbatim}}
	The Twitter posts matching the search term \#Libya are likewise all described
	in the output document. The description for the post from our example 
	%abbreviated \texttt{m} 
	results in the following triples:
	{\small\begin{verbatim}<http://km.aifb.kit.edu/services/twitterwrap/statuses/
	show/46619460060196865\#id> 
	   foaf:page <http://twitter.com/SenJohnMcCain/statuses/
	      46619460060196865>;
	   dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;
	   geo:long "8.411879" ;
	   foaf:maker <http://km.aifb.kit.edu/services/twitterwrap/users/
		    show?screen\_name=SenJohnMcCain\#id> ;
	   dc:description "Arab League calls for no-fly zone in \#Libya 
	      http://\newline t.co/ZsLNIWa" . \end{verbatim}}     
\end{enumerate}

@@

We provide an implementation of our approach in the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}}.

The implementation is based on a set of existing components: 
\begin{itemize}
\item Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}, a RESTful API which delivers search results in JSON. The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors. The messages themselves are described by their content, publishing date, authors
and optionally a geographic location.

\item The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true}. To keep the input size for the next steps manageable, only the first 50 words of the referenced sites are used. The content
retrieved from external websites is beautified for our purpose removing
HTML-tags and scripting elements using the CyberNeko Java HTML Parser
Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.

\item The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analysed text. It represents a state-of-the-art annotation tool and was chosen as it allows for finding entities not from some tool-specific knowledge base but from DBpedia, which is one of the most widely used data sources on the Linked Data Web.

\item The system generates and outputs an RDF document in RDF/XML Syntax containing a
description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. 
%It describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}. A single Twitter message is described by its individual page using the \texttt{foaf:page} predicate. The date and time the message has been posted is specified using the \texttt{dc:date} predicate. The message's content is annotated using \texttt{dc:description}, while the geographic location of the message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that uses RDF to describe information related to a Twitter user which has previously been implemented here at the institute as the message creators URI.

@@

\end{itemize}

%The example Twitter message given in the previous section is represented in
%the output of the Twitter Search Wrapper as follows:\newline
%\linebreak
%\texttt{<rdf:Description
%rdf:about="http://km.aifb.kit.edu/services/\newline
%Twitterwrap/statuses/show/1234567890\#id">\newline
%	<foaf:page
%	rdf:resource="http://Twitter.com/sample\_user\_12345/\newline
%	statuses/1234567890"/>\newline
%	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
%	<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
%	<foaf:maker
%	rdf:resource="http://km.aifb.kit.edu/services/\newline
%	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline
%	<dc:description>\newline Just returned from a wonderful holiday in \#ka.
%	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
%	</dc:description>\newline
%	</rdf:Description>\newline}
%	\linebreak
%Furthermore the mappings to DBpedia articles returned by the Wikifier
%are represented in the output document. In the Twitter Search Wrapper the
%representation is done the following way, again using the introductory
%example from the previous section:\newline
%\linebreak
%	\texttt{<rdf:Description rdf:about=""/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
%	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
%	Karlsruhe\_Institute\_of\_Technology"/>}\newline
%	\texttt{</rdf:Description>}\newline

@@

We have evaluated our approach to assess whether the entities which are found as related to a specific hashtag are stable over time.

@@

We have conducted experiments on a set of queries which were identified to be hashtags which are frequently used on Twitter.
To obtain these, we have sampled the Twitter message feed using Twitter's
Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
top-50 hashtags dervied from the aggregate sample are listed in Table
\ref{tbl:hashtags}, count is the number of times we encountered them during the
collection period.

@@

\small

@@

\#ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
\#np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
\#nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
\#winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
\#fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\
\#rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
\#mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
\#blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
\#tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
\#thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
\#fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
\#teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
\#iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
\#bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
\#news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
\#jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
\#libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
\#followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\
\#partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
\#sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\
\#damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
\#tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
\#soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
\#nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\
\#quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\

@@

\#nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
\#quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
\#shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
\#jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
\#carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
